\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2020-11-09 analysis/paper/paper.Rmd
added percent to species table
not sure if its helpful but might be

knitr::kable(x = df, 
             # set column names
             col.names = c("Taxon code",
                           "Scientific name (*Genus species*)",
                           "Common name",
                           "Number of spectra"),
             # center align text in the columns
             align = c("l", "l", "l", "l"),
             format = "simple") 
  # show which rows are grouped together for genus classes visibly in table?

@@

We conclude that HS data allow you to get __ accuracy
Hopes for outcomes

@@

Map to illustrate the NEON sites and domains with data that we used in this study.

>>>>

df$count_percent <- round((df$count / sum(df$count)) * 100, digits = 1)

knitr::kable(x = df, 
             # set column names
             col.names = c("Taxon code",
                           "Scientific name (*Genus species*)",
                           "Common name",
                           "Number of spectra",
                           "Percent (%) of total"),
             # center align text in the columns
             align = c("l", "l", "l", "c", "c"),
             format = "simple") 
  # show which rows are grouped together for genus classes visibly in table?

@@

We conclude that NEON hyperspectral data allow you to achieve 55% or 60% accuracy when classifying species or genus classes.

Hopes for outcomes

@@

Map to illustrate where NEON data were collected that we used in this study. Black points represent NEON site locations where *in-situ* plant observations were collected along with airborne remote sensing flights. NEON domains containing each respective site are
